Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-07 paper.tex
through a random circuit into the paper

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}

@@

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Provides}\\ \footnotesize{inductive bias}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white]{{\footnotesize Makes tractable}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
  \end{figure}

@@

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
Now, if we equipped our agent with a full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates,
as well as 2 or 4 input multiplexers.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{circuitTables}, top).
We compare  with four baselines on 250 held-out circuits:
No NN, which lesions $q$;
RF/DC,
which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a $q$ only from samples from the fixed generative model --
this is how RobustFill and DeepCoder are trained;
PCFG, which lesions $q$, fixes $\mathcal{D}$, and learns only $\theta$ (so it is analogous to learning the parameters of a PCFG);
and Enum, which does no learning and just enumerates a large frontier.
\begin{figure}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  84\% solved&76\%& \\
  $0.9$ sec&  1.1
  \\\bottomrule
\end{tabular}
\end{figure}

>>>>

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{circuitikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}

@@

    \draw [->,thick,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,thick,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
\caption{Our algorithm solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
  \end{figure}

@@

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
Now, if we equipped our agent with a full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates,
as well as 2 or 4 input multiplexers.
\system observes the input/output truth table of the circuits.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{circuitTables}, top).
We compare  with four baselines on 250 held-out circuits:
No NN, which lesions $q$;
RF/DC,
which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a $q$ only from samples from the fixed generative model --
this is how RobustFill and DeepCoder are trained;
PCFG, which lesions $q$, fixes $\mathcal{D}$, and learns only $\theta$ (so it is analogous to learning the parameters of a PCFG);
and Enum, which does no learning and just enumerates a large frontier.
\begin{figure}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  84\% solved&76\%& 63\%&62\%&62\%\\
  $0.9$ sec&  1.1&1.2&1.3&1.3
  \\\bottomrule
\end{tabular}
\caption{Top: \% held-out Boolean circuits solved by \system and baselines w/ 5sec timeout. Bottom: average search time.}
\end{figure}

\begin{figure}
  \begin{circuitikz} \draw
(0,2) node[and port] (myand1) {}
(0,0) node[and port] (myand2) {}
(2,1) node[xnor port] (myxnor) {}
(myand1.out) -- (myxnor.in 1)
(myand2.out) -- (myxnor.in 2);
\end{circuitikz}
  \end{figure}
